---
title: "Percy's Assignment"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: c('both')
---

Welcome to my assignment.

```{r}
d <- read.csv("data/homes.csv")
data <- d[1:50,]
```
This is the dataset which shows home sale statistics. It contains 50 home sales, with selling price, asking price, living space, rooms, bedrooms, bathrooms, age, acreage, taxes.

We show descriptive statistics of the selling prices and living spaces as below:
```{r}
summary(data[,c(1,3)])
```

Now we add plots of distribution (histogram) of selling price and living space.
```{r}
hist(data$Sell, xlab = "Selling Price", main = "Distribution of Selling Price")
hist(data$Living, xlab = "Living Space", main = "Distribution of Living Space")
```

Now we add scatter plot between selling price and living space.
```{r}
plot(data$Living, data$Sell, type="p", main = "Scatter plot btw selling price and living space", ylab = "Selling Price", xlab = "Living Space")
```

Now we run a simple linear regression and output its summary:
```{r}
lmodel <- lm(Sell~Living, data)
summary(lmodel)
```
We can see that Selling Price is positively correlated to Living Space. The linear regression shows that the slope of price to space relationship is `r lmodel$coefficients[2]`. i.e. Every time living space increases by 1, the selling price tends to increase by `r lmodel$coefficients[2]`.

---
title: "Percy's Assignment"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: c('both')
---

Welcome to my assignment.

```{r}
d <- read.csv("data/homes.csv")
data <- d[1:50,]
```
This is the dataset which shows home sale statistics. It contains 50 home sales, with selling price, asking price, living space, rooms, bedrooms, bathrooms, age, acreage, taxes.

We show descriptive statistics of the selling prices and living spaces as below:
```{r}
summary(data[,c(1,3)])
```

Now we add plots of distribution (histogram) of selling price and living space.
```{r}
hist(data$Sell, xlab = "Selling Price", main = "Distribution of Selling Price")
hist(data$Living, xlab = "Living Space", main = "Distribution of Living Space")
```

Now we add scatter plot between selling price and living space.
```{r}
plot(data$Living, data$Sell, type="p", main = "Scatter plot btw selling price and living space", ylab = "Selling Price", xlab = "Living Space")
```

Now we run a simple linear regression and output its summary:
```{r}
lmodel <- lm(Sell~Living, data)
summary(lmodel)
```
We can see that Selling Price is positively correlated to Living Space. The linear regression shows that the slope of price to space relationship is `r lmodel$coefficients[2]`. i.e. Every time living space increases by 1, the selling price tends to increase by `r lmodel$coefficients[2]`.

Now we will publish the site.
This time we will.
aaaa
